PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$

### 2015-04-20 qfenv_paper/ApJ submission/referee_response2.txt

Dear Editor,

We once again thank the referee for the thorough review of our work and
for the constructive report.

Please find below responses to the referee's comment along with changes
made to our paper.

Thank you, 
ChangHoon Hahn

================================================================================
        April 11, 2015

        Mr. ChangHoon Hahn
        Center for Cosmology and Particle Physics
        New York University
        4 Washington Place
        New York, NY 10003

        Title: PRIMUS: Effects of Galaxy Environment on the Quiescent
        Fraction Evolution at z < 0.8, ApJ97613R1

        Dear Mr. Hahn,

        The revised version of your paper cited above was sent back to
        the referee, who is mostly satisfied with the changes you have
        made. He/she just has a few remaining comments (appended below),
        which I would like you to take into consideration.

        When you resubmit the manuscript, please include a detailed
        cover letter containing the (mandatory) listing of the changes
        you've made to the text and your responses to the report.

        Click the link below to upload your revised manuscript; 
        http://apj.msubmit.net/cgi-bin/main.plex?el=A1Ew7DXK1A4CfGS3J7A9ftduFQ0I1nKsyQ3P8J1nY5FIQZ
        Alternatively, you may also log into your account at the EJ
        Press web site, http://apj.msubmit.net. Please use your user's
        login name: chahah. You can then ask for a new password via the
        Unknown/Forgotten Password link if you have forgotten your
        password.

        Reviewers find it helpful if the changes in the text of the
        manuscript are easily distinguishable from the rest of the text.
        Therefore we ask you to print changes in bold face. The
        highlighting can be removed easily after the review.

        The Astrophysical Journal has adopted a new policy that
        manuscript files become inactive, and are considered to have
        been withdrawn, six months after the most recent referee's
        report goes to the authors, provided a revised version has not
        been received by that time.

        If you have any questions, feel free to contact me.

        Sincerely,
        Lee Armus
        ApJ Scientific Editor
        California Institute of Technology
        apjla@ipac.caltech.edu

        ---------------------------------------------------------------------- 
        Referee Report
        Reviewer's Comments:

        I have looked at the changes. I think the argument about the
        cosmic variance affecting the quiescent fraction is overstated -
        some of it irrelevant. The cosmic variance has a much larger
        effect on the number counts than on the fraction of quiescent
        galaxies in high density environments; the latter is not
        estimated by cosmic variance calculators/equations. I agree the
        jack-knife method may underestimate the errors. Alternatively
        perhaps the stellar mass limits are not strict enough when
        estimating the quiescent fraction, since the 'missed galaxies'
        will preferentially be quiescent. I recommend the authors think
        about this a bit more; or at least remove the text about the
        cosmic variance. This should equally affect the >10^10 sample
        for the z=0.3 bin.

RESPONSE: 
We have removed the text discussing the cosmic variance.

        You now undersell PRIMUS versus zCOSMOS. The targeting
        completeness for zCOSMOS is much lower, see Fig. 5 of Lilly et
        al. 2009 for the 10k sample. What is most relevant is combined
        targeting completeness and redshift success - even a rough
        estimate for zCOSMOS would be a useful comparison - and would be
        a favourable metric for PRIMUS I think.

RESPONSE: 
We now explicitly mention the targeting completeness (spatial sampling
rate) of zCOSMOS in addition to the redshift completeness and list an
estimate of the overall completeness rate of zCOSMOS mentioned in Knobel
et al. (2012).

--------------------------------------------------------------------------------
OTHER CHANGES:

- We now state that Iovino et al. (2010) remark that the uncertainties
  in the quiescent fraction fits are too large to make any conclusions
  about the quiescent fraction evolution.

### 2015-04-20 qfenv_paper/ApJ submission/qf_environment.tex
Referee Report #2

them. {\bf In other words}, in the recent Universe a substantial fraction of the

@@

\begin{figure*}
    \begin{center}
        \leavevmode
	\includegraphics[scale=0.475]{fig1.pdf}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to the \cite{Coil:2011aa}. For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.}

@@

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with {\bf a time dependent dust attenuation curve of \cite{Charlot:2000aa} and }other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. {\bf For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.}

@@

    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges. A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. {\bf Galaxies with $n_{\mathrm{env}} = 0.0$ are in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
{\bf We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
and $H_\mathrm{ap}$ are comoving distances.} We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Finally, we measure the environment for each galaxy in our galaxy
sample by counting the number of EDP galaxies, $n_{\mathrm{env}}$, with RA,
Dec, and $z$ within our cylindrical aperture centered around
it. $n_{\mathrm{env}}$ accounts for the statistical weights of the EDP
galaxies. 
For our galaxy sample, the expected $n_{\mathrm{env}}$ given the uniform number density in 
each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\mathrm{env}} \rangle = 1.3$. 
Once we obtain environment measurements for all the galaxies
in our galaxy sample, {\bf we classify galaxies with $n_{\mathrm{env}} = 0.0$
to be in ``low" environment densities} and galaxies with $n_{\mathrm{env}} > 3$
to be in ``high" environment densities. The high environment cutoff was
selected in order to reduce contamination from galaxies in low
environment densities while maintaining sufficient statistics. In
Section \ref{sec:env_qf_evol} we will also explore higher density
cutoffs for $n_{\mathrm{env}}$.

@@

In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. We classify {\bf galaxies with $n_{\mathrm{env}} = 0.0$ to be in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
{\bf classified as low environment when $n_{\mathrm{env}} = 0.0$ and }as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

{\bf We note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, we find no significant difference between $f_\mathrm{Q}$ in low and high density environments. Similar quiescent/red fraction studies (e.g. \citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$. However we note that, at $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample. As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the PRIMUS fields XMM-SXDS and XMM-CFHTLS are adjacent fields. A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$. This estimate does not take into account the unique geometry of the PRIMUS fields or the edge-cuts, which only increase the cosmic variance uncertainties. Therefore, the quiescent fraction comparison at $z \sim 0.3$ for $\mathcal{M}_{*} < 10^{10} \mathcal{M}_\odot$ cannot be accurately made from our PRIMUS sample.}

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig5.pdf, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. {\bf For the environment cut-offs ($n_{\mathrm{env}} =0.0 $ for low }and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

@@

Because our fixed aperture definition of environment is susceptible to
contamination due to PRIMUS redshift errors, we consider in Figure
\ref{fig:qffit_comp} more stringent high density environment
classifications, extending the cut off to $n_{\mathrm{env}} > 5$ and
$7$ (specified in the top right legend and represented by the color of
the shading). Aside from the increase in uncertainties that accompany
the decrease in sample size of the purer high environment sample, we
find an extension of the $f_{\mathrm{Q}}$ difference between the
environments we stated earlier. A more stringent high environment
classification significantly increases the overall
$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$, which rises monotonically with
the $n_{\mathrm{env}}$ limit.

@@

% Removed in order to tone down the criticism of 
%However, even without the correction (not shown), in their best-fit $f_{\mathrm{Q}}$ results, the same evolutionary trends mentioned above are observed.

While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics. In addition, our sample covers a larger portion of the sky. Our SDSS-{\em GALEX} sample covers $2,505 \;\mathrm{deg}^2$. More comparably, our PRIMUS sample covers $5.5 \;\mathrm{deg}^2$, over 3 times the sky coverage of zCOSMOS ($1.7 \;\mathrm{deg}^2$). Furthermore, our PRIMUS sample is constructed from five independent fields which allows us to significantly reduce the effects of cosmic variance.

>>>>

them. In other words, in the recent Universe a substantial fraction of the

@@

\begin{figure*}
    \begin{center}
        \leavevmode
	\includegraphics[scale=0.475]{fig1.pdf}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to \cite{Coil:2011aa}. For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.

@@

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with a time dependent dust attenuation curve of \cite{Charlot:2000aa} and other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For details on the effects of prior parameter choices of iSEDfit on physical properties of galaxies we refer readers to the Appendix of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.

@@

    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges. A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Galaxies with $n_{\mathrm{env}} = 0.0$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
and $H_\mathrm{ap}$ are comoving distances. We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Finally, we measure the environment for each galaxy in our galaxy
sample by counting the number of EDP galaxies, $n_{\mathrm{env}}$, with RA,
Dec, and $z$ within our cylindrical aperture centered around
it. $n_{\mathrm{env}}$ accounts for the statistical weights of the EDP
galaxies. 
For our galaxy sample, the expected $n_{\mathrm{env}}$ given the uniform number density in 
each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\mathrm{env}} \rangle = 1.3$. 
Once we obtain environment measurements for all the galaxies
in our galaxy sample, we classify galaxies with $n_{\mathrm{env}} = 0.0$
to be in ``low" environment densities and galaxies with $n_{\mathrm{env}} > 3$
to be in ``high" environment densities. The high environment cutoff was
selected in order to reduce contamination from galaxies in low
environment densities while maintaining sufficient statistics. In
Section \ref{sec:env_qf_evol} we will also explore higher density
cutoffs for $n_{\mathrm{env}}$.

@@

In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. We classify galaxies with $n_{\mathrm{env}} = 0.0$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and classified as low environment when $n_{\mathrm{env}} = 0.0$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

{\bf We note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, we find no significant difference between $f_\mathrm{Q}$ in low and high density environments. Similar quiescent/red fraction studies (e.g. \citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$. Our classification of star-forming/quiescent galaxies may contribute to this discrepancy with other quiescent fraction studies. We also note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample. As a result our jack-knife method, which calculates uncertainty by excluding one PRIMUS field at a time, may underestimate the uncertainty thereby making an accurate comparison difficult at low masses. For our analysis, we focus on $\mathcal{M}_* > 10^{10} \mathcal{M}_\odot$. }

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig5.pdf, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. For the environment cut-offs ($n_{\mathrm{env}} =0.0 $ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

@@

However, the uncertainties in the PRIMUS redshifts may contaminate 
our fixed aperture measurements of galaxy environment. Consequently, we consider in Figure
\ref{fig:qffit_comp} more stringent high density environment
classifications, extending the cut off to $n_{\mathrm{env}} > 5$ and
$7$ (specified in the top right legend and represented by the color of
the shading). Aside from the increase in uncertainties that accompany
the decrease in sample size of the purer high environment sample, we
find an extension of the $f_{\mathrm{Q}}$ difference between the
environments we stated earlier. A more stringent high environment
classification significantly increases the overall
$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$, which rises monotonically with
the $n_{\mathrm{env}}$ limit.

@@

%However, even without the correction (not shown), in their best-fit $f_{\mathrm{Q}}$ results, the same evolutionary trends mentioned above are observed.
